---
title: "Anatomy and architecture summary"
author: "Malo"
date: "2025-01-17"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    toc_depth: 5
    theme: cosmo
---

```{r setup, include=FALSE}
library(ggplot2)
library(jpeg)
library(purrr)
library(psych)
library(lme4)
library(multcomp)
library(multcompView)


library(tidyverse)

```

Created from anat_archi_summary_v1.Rmd


# Creating datasets
## Anatomy
### Image dimensions

```{r}
#####Getting image dimensions####
# list JPG files in a directory
square_files <- list.files(path = "square", pattern = "\\.jpg$", full.names = TRUE)


get_image_dimensions <- function(image_path) {
  img <- readJPEG(image_path, native = TRUE)  # Load the image
  list(
    file = basename(image_path),              # File name
    width_px = attr(img, "dim")[2],              # Width
    height_px = attr(img, "dim")[1]              # Height
  )
}

#function to all images
image_dimensions <- lapply(square_files, get_image_dimensions)

#get data frame
image_dimensions_df <- do.call(rbind.data.frame, image_dimensions)

#####Making variables in good format####

image_dimensions_df$id_complete <- gsub("_square\\.jpg$", "", image_dimensions_df$file)

image_dimensions_df$id_amap <- substr(image_dimensions_df$id_complete, 1, 4)


image_dimensions_df$id_complete2 <- ifelse(
  nchar(image_dimensions_df$id_complete) == 28,
  paste0(substr(image_dimensions_df$id_complete, 1, 12), "0", substr(image_dimensions_df$id_complete, 13, nchar(image_dimensions_df$id_complete))),
  image_dimensions_df$id_complete
)
image_dimensions_df$id_complete3 <- ifelse(
  nchar(image_dimensions_df$id_complete2) == 30,
  paste0(substr(image_dimensions_df$id_complete2, 1, 12), "0", substr(image_dimensions_df$id_complete2, 13, nchar(image_dimensions_df$id_complete2))),
  image_dimensions_df$id_complete2
)


image_dimensions_df$id_complete4 <- gsub("Tige", "T", image_dimensions_df$id_complete3)
image_dimensions_df$id_complete5 <- gsub("Racine", "R", image_dimensions_df$id_complete4)


image_dimensions_df$id_complete6 <- gsub("-", "_", image_dimensions_df$id_complete5)

split_names <- strsplit(image_dimensions_df$id_complete6, "_")

image_dimensions_df$site <- sapply(split_names, function(x) x[2])      # Second element (T1)
image_dimensions_df$species <- sapply(split_names, function(x) x[3])  # Third element (Ho2)
image_dimensions_df$id_lucas <- sapply(split_names, function(x) x[4]) # Fourth element (03)
image_dimensions_df$organ <- sapply(split_names, function(x) x[5])    # Fifth element (T)
image_dimensions_df$zoom <- sapply(split_names, function(x) x[6])     # Sixth element (X200)
image_dimensions_df$coupe_µm <- sapply(split_names, function(x) x[7]) # Seventh element (09µm)


image_dimensions_df$site_type <- substr(image_dimensions_df$site, 1, 1)  # First character (T)
image_dimensions_df$site_replicate <- substr(image_dimensions_df$site, 2, nchar(image_dimensions_df$site))  # Remaining characters (1)


image_dimensions_df$micro <- ifelse(grepl("[a-z]", image_dimensions_df$site_type), 1, 0)

image_dimensions_df$site_type <- toupper(image_dimensions_df$site_type)


image_dimensions_df$species_name <- substr(image_dimensions_df$species, 1, 2)  # First two characters (e.g., "Ho")
image_dimensions_df$species_site_replicate <- substr(image_dimensions_df$species, 3, nchar(image_dimensions_df$species))  # Remaining characters (e.g., "1")


image_dimensions_df$width_µm <- image_dimensions_df$width_px / 1.9111
image_dimensions_df$height_µm <- image_dimensions_df$height_px / 1.9111

image_dimensions_df$image_surface_µm2 <- image_dimensions_df$width_µm * image_dimensions_df$height_µm

#####Final dataset####
anat <- data.frame(
  file = image_dimensions_df$file,
  id_complete = image_dimensions_df$id_complete6,
  image_surface_µm2 = image_dimensions_df$image_surface_µm2,
  id_amap = image_dimensions_df$id_amap,
  number = image_dimensions_df$id_lucas,
  site = image_dimensions_df$site,
  site_type = image_dimensions_df$site_type,
  site_replicate = image_dimensions_df$site_replicate,
  species_site_replicate = image_dimensions_df$species,
  species = image_dimensions_df$species_name,
  species_replicate = image_dimensions_df$species_site_replicate,
  micro = image_dimensions_df$micro,
  organ = image_dimensions_df$organ,
  
  
  stringsAsFactors = FALSE
)


```

### Calculating vessel conductivity, clusters, size, diameter...

```{r}
vessel <- read.csv(file = "vessel_4.csv", header = T, stringsAsFactors = T)
vessel$file <- vessel$Label
anat <- read.csv(file = "anat_3.csv", header = T, stringsAsFactors = T)
anat$id_amap <- as.character(anat$id_amap)
#Files will change if data is updated

#####Getting proper surface by getting rid of big empty areas####

vessel$id_amap <- as.factor(substr(vessel$file, 1, 4))

#####Clusters####
# clustering function
cluster_vessels <- function(data) {
#Compute radii
  data$Radius <- sqrt(data$Area / pi)
  data$Radius_enhanced <- data$Radius + 4.5
  
#distance between every vessel
distances <- as.matrix(dist(data[, c("X", "Y")], method = "euclidean"))
radius_matrix <- outer(data$Radius_enhanced, data$Radius_enhanced, "+")
perimeter_distances <- distances - radius_matrix
  
data$Cluster <- 0
cluster_id <- 1
  
#Clustering
  repeat {
    changes <- FALSE
    
    for (i in seq_len(nrow(perimeter_distances))) {
      if (data$Cluster[i] == 0) {
        data$Cluster[i] <- cluster_id
        nearby <- which(perimeter_distances[i, ] <= 0)
        data$Cluster[nearby] <- cluster_id
        changes <- TRUE
        cluster_id <- cluster_id + 1
      }
    }
    
    for (i in seq_len(nrow(perimeter_distances) - 1)) {
      for (j in seq(i + 1, nrow(perimeter_distances))) {
        if (perimeter_distances[i, j] <= 0) {
          if (data$Cluster[i] != data$Cluster[j]) {
            old_cluster <- data$Cluster[j]
            new_cluster <- data$Cluster[i]
            data$Cluster[data$Cluster == old_cluster] <- new_cluster
            changes <- TRUE
          }
        }
      }
    }
    
    if (!changes) break
  }
  
  return(data)
}

#Group by `id_amap` and apply clustering
vessel <- vessel %>%
  group_by(id_amap) %>%
  group_split() %>%
  map_dfr(cluster_vessels)



#####Getting rid of extremes####
vessel_mean <- vessel %>%
  group_by(id_amap) %>%
  summarize(mean = mean(Area))

vessel_extreme <- vessel %>%
  filter(Area > 1200)


vessel_extreme_sum <- vessel_extreme %>%
  group_by(id_amap) %>%
  summarize(sum = sum(Area))

vessel_extreme_sum$id_amap <- as.character(vessel_extreme_sum$id_amap)
anat$id_amap <- as.character(anat$id_amap)
vessel_extreme_sum <- vessel_extreme_sum %>%
  full_join(anat, by = "id_amap")

vessel_extreme_sum$sum[is.na(vessel_extreme_sum$sum)] <- 0
vessel_extreme_sum$image_surface_rectified_µm2 <- vessel_extreme_sum$image_surface_µm2 - vessel_extreme_sum$sum

vessel_extreme_sum <- vessel_extreme_sum %>%
  dplyr::select(id_amap, image_surface_rectified_µm2)

anat <- anat %>%
  left_join(vessel_extreme_sum, by = "id_amap")

#####Calculating mean, standard deviation, sum, count, dh####
#Getting rid of big vessels
vessel_1200 <- vessel %>%
  select(id_amap, Area, Perim., Cluster) %>%
  filter(Area <= 1200) %>%
  mutate(diameter = 2*sqrt(Area/pi),
         d4 = diameter^4)

vessel_summary_pre <- vessel_1200 %>%
  group_by(id_amap) %>%
  distinct(Cluster) %>%
  summarize(count_cluster = n())

  
vessel_summary_pre2 <- vessel_1200 %>%
  group_by(id_amap) %>%
  summarize(mean_vessel_size_µm2 = mean(Area),
            std_dev_vessel_size_µm2 = sd(Area),
            mean_vessel_perim_µm = mean(Perim.),
            std_dev_perim_µm = sd(Perim.),
            sum_vessel_area_µm2 = sum(Area),
            dh = (sum(d4)/n())^0.25,
            count_vessel = n()
            ) 

vessel_summary <- vessel_summary_pre2 %>%
  left_join(vessel_summary_pre, by = "id_amap") %>%
  mutate(vessel_grouping = count_vessel / count_cluster)

#####Calculating vessel density and Kth####
vessel_summary <- anat %>%
  select(id_amap, image_surface_rectified_µm2) %>%
  left_join(vessel_summary, by = "id_amap")

vessel_summary$image_surface_rectified_mm2 <- vessel_summary$image_surface_rectified_µm2 / 1000000

vessel_summary$vessel_density_per_mm2 <- vessel_summary$count_vessel / vessel_summary$image_surface_rectified_mm2
vessel_summary$vessel_density_per_m2 <- vessel_summary$vessel_density_per_mm2 * 10^6
vessel_summary$dh_m <- vessel_summary$dh * 10^-6
vessel_summary$vessel_area <- vessel_summary$sum_vessel_area_µm2 / vessel_summary$image_surface_rectified_µm2


#Getting Kth

water_density <- 998.2
water_viscosity <- 1.002*10^-9
hagen_poiseuille <- (pi * water_density) / (128 * water_viscosity)

vessel_summary$Kth <- hagen_poiseuille * vessel_summary$vessel_density_per_m2 * vessel_summary$dh_m^4




plot(vessel_summary$vessel_density_per_mm2, vessel_summary$Kth)

summary(vessel_summary)
#####
write.csv(vessel_summary, file = "vessel_summary_4.csv")
write.csv(anat, file = "anat_6.csv")
```

### Binding stem and root data for every individual

```{r}
anat <- read.csv(file = "anat_6.csv", header = T, stringsAsFactors = T)

#####Preparing the data####
anat <- anat %>%
  select(-X.1, -X)

anat$id_amap <- as.character(anat$id_amap)
vessel_summary$id_amap <- substr(image_dimensions_df$id_complete, 1, 4)

anat <- anat %>%
  left_join(vessel_summary, by = "id_amap")
anat$number <- as.factor(anat$number)
anat$count_vessel <- as.numeric(anat$count_vessel)
anat$id_amap <- as.numeric(anat$id_amap)
#####Creating stem and root datasets####
numerical_cols <- c("image_surface_µm2", "image_surface_rectified_µm2.x", 
                    "mean_vessel_size_µm2", "std_dev_vessel_size_µm2", "mean_vessel_perim_µm", 
                    "std_dev_perim_µm", "sum_vessel_area_µm2", "count_vessel", "count_cluster", "vessel_grouping", "dh", 
                    "image_surface_rectified_mm2", "vessel_density_per_mm2", "vessel_density_per_m2", 
                    "dh_m", "vessel_area", "Kth")

anat_Racine <- anat %>% 
  filter(organ == "R") %>%
  dplyr::select(all_of(numerical_cols), number) %>%
  rename_with(~ paste0(., "_Racine"), all_of(numerical_cols))

anat_Tige <- anat %>% 
  filter(organ == "T") %>%
  dplyr::select(all_of(numerical_cols), number) %>%
  rename_with(~ paste0(., "_Tige"), all_of(numerical_cols))
#####Binding root and stem datasets and selecting variables####
anat_Tige_Racine <- anat_Tige %>%
  full_join(anat_Racine, by = "number")
#keeping metadata aside
anat_metadata <- anat %>%
  dplyr::select(number, site, site_type, site_replicate, species_site_replicate, species, species_replicate, micro) %>%
  distinct(number, site, site_type, site_replicate, species_site_replicate, species, species_replicate, micro)


anat_combined <- anat_metadata %>%
  left_join(anat_Tige_Racine, by = "number")

one_ninety <- read.csv("1_90.csv", header = T, stringsAsFactors = T)
anat_combined$number <- as.character(anat_combined$number)
one_ninety$number <- as.character(one_ninety$number)

anat_combined <- anat_combined %>%
  full_join(one_ninety, by = "number")
anat_combined$number <- as.integer(anat_combined$number)
#####
write.csv(anat_combined, "anat_combined_3.csv")
```

## Architecture

### Binding anatomy dataset with architecture

```{r}
archi <- read.csv("archi_2.csv", header =T, stringsAsFactors = T)
anat_combined <- read.csv("anat_combined_3.csv", header = T, stringsAsFactors = T)
metadata <- read.csv("metadata.csv", header = T, stringsAsFactors = T)

#####Joining datasets####
metadata$number <- as.character(metadata$number)
archi$number <- archi$num
anarchi <- archi %>%
  dplyr::select(-X, -code, -species, -site_type, -site_replicate, -site, -micro) %>%
  full_join(anat_combined, by = "number") %>%
  dplyr::select(-X)

anarchi$number <- as.character(anarchi$number)
anarchi <- anarchi %>%
  select(-site,-site_type, -site_replicate, -species_site_replicate, -species, -species_replicate, -micro) %>%
  left_join(metadata, by = "number")

anarchi <- anarchi %>%
  select(-num)
anarchi <- anarchi %>%
  select(number, site, site_type, site_replicate, species_site_replicate, species, species_replicate, micro, everything())
#####
write.csv(anarchi, "anarchi_3.csv")
```
### Creating dataset for each species
```{r}
anarchi <- read.csv(file = "anarchi_3.csv", header = T, stringsAsFactors = T)
anarchi_Ho <- anarchi %>%
  filter(species == "Ho")
anarchi_Fe <- anarchi %>%
  filter(species == "Fe")
anarchi_Ft <- anarchi %>%
  filter(species == "Ft")
```


# Data exploration
## Correlations overview
### Fumana ericoides
```{r}
pairs.panels(anarchi_Fe[,c("Kth_Tige", "vessel_density_per_mm2_Tige", "dh_Tige", "site_type",
                        "diam_tig_princip_mm", "diam_rac_pivot_mm",
                        "diam_rac_lat_mm", "diam_tig_lat_mm",
                        "empreinte_photo_mm", "y_photo_mm")],
             method = "spearman", # correlation method
             hist.col = "lightgreen",
             density = TRUE,  # show density plots
             ellipses = FALSE # show correlation ellipses
)
```

### Fumana thymifolia
```{r}
pairs.panels(anarchi_Ft[,c("Kth_Tige", "vessel_density_per_mm2_Tige", "dh_Tige", "site_type",
                        "diam_tig_princip_mm", "diam_rac_pivot_mm",
                        "diam_rac_lat_mm", "diam_tig_lat_mm",
                        "empreinte_photo_mm", "y_photo_mm")],
             method = "spearman", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = FALSE # show correlation ellipses
)
```

### Helianthemum oelandicum
```{r}
pairs.panels(anarchi_Ho[,c("Kth_Tige", "vessel_density_per_mm2_Tige", "dh_Tige",
                        "diam_tig_princip_mm", "diam_rac_pivot_mm",
                        "diam_rac_lat_mm", "diam_tig_lat_mm",
                        "empreinte_photo_mm", "y_photo_mm")],
             method = "spearman", # correlation method
             hist.col = "orange",
             density = TRUE,  # show density plots
             ellipses = FALSE # show correlation ellipses
)
```

## Architecture
### Fumana ericoides
#### Site models
##### Diamètre tige principale

```{r}
mod_fe_1 <- lm(diam_tig_princip_mm ~ site_type, data = anarchi_Fe)
mod_fe_1_aov <- aov(diam_tig_princip_mm ~ site_type, data = anarchi_Fe)

anova(mod_fe_1)
plot(mod_fe_1)

summary(mod_fe_1)
boxplot(diam_tig_princip_mm ~ site_type, data = anarchi_Fe)


tuk_fe_1 <- glht(mod_fe_1_aov, linfct = mcp(site_type = "Tukey"))
# test de Tukey:
summary(tuk_fe_1) 

tuk.cld_fe_1 <- cld(tuk_fe_1, decreasing = TRUE)   
tuk.cld_fe_1 $mcletters$Letters
```

##### Conicité

```{r}
#######
mod_fe_2 <- lm(conicite_mm ~ site_type, data = anarchi_Fe)
mod_fe_2_aov <- aov(conicite_mm ~ site_type, data = anarchi_Fe)

anova(mod_fe_2)
plot(mod_fe_2)
```

##### Profondeur du pivot

```{r}
#######
mod_fe_3 <- lm(prof_pivot_mm ~ site_type, data = anarchi_Fe)
mod_fe_3_aov <- aov(prof_pivot_mm ~ site_type, data = anarchi_Fe)

anova(mod_fe_3)
plot(mod_fe_3)

summary(mod_fe_3)
boxplot(prof_pivot_mm ~ site_type, data = anarchi_Fe)


tuk_fe_3 <- glht(mod_fe_3_aov, linfct = mcp(site_type = "Tukey"))
# test de Tukey:
summary(tuk_fe_1) 

tuk.cld_fe_3 <- cld(tuk_fe_1, decreasing = TRUE)   
tuk.cld_fe_3 $mcletters$Letters
```



### Fumana thymifolia
#### Site models
##### Diamètre tige principale

```{r}
mod_ft_1 <- lm(diam_tig_princip_mm ~ site_type, data = anarchi_Ft)
mod_ft_1_aov <- aov(diam_tig_princip_mm ~ site_type, data = anarchi_Ft)

anova(mod_ft_1)
plot(mod_ft_1)

summary(mod_ft_1)
boxplot(diam_tig_princip_mm ~ site_type, data = anarchi_Ft)


tuk_ft_1 <- glht(mod_ft_1_aov, linfct = mcp(site_type = "Tukey"))
# test de Tukey:
summary(tuk_fe_1) 

tuk.cld_ft_1 <- cld(tuk_ft_1, decreasing = TRUE)   
tuk.cld_ft_1 $mcletters$Letters
```

##### Conicité

```{r}
mod_ft_2 <- lm(conicite_mm ~ site_type, data = anarchi_Ft)
mod_ft_2_aov <- aov(conicite_mm ~ site_type, data = anarchi_Ft)

anova(mod_ft_2)
plot(mod_ft_2)

summary(mod_ft_2)
boxplot(conicite_mm ~ site_type, data = anarchi_Ft)


tuk_ft_2 <- glht(mod_ft_2_aov, linfct = mcp(site_type = "Tukey"))
# test de Tukey:
summary(tuk_ft_2) 

tuk.cld_ft_2 <- cld(tuk_ft_2, decreasing = TRUE)   
tuk.cld_ft_2 $mcletters$Letters
```

##### Profondeur du pivot

```{r}
mod_ft_3 <- lm(prof_pivot_mm ~ site_type, data = anarchi_Ft)
mod_ft_3_aov <- aov(prof_pivot_mm ~ site_type, data = anarchi_Ft)

anova(mod_ft_3)
plot(mod_ft_3)

summary(mod_ft_3)
boxplot(prof_pivot_mm ~ site_type, data = anarchi_Ft)


tuk_ft_3 <- glht(mod_ft_3_aov, linfct = mcp(site_type = "Tukey"))
# test de Tukey:
summary(tuk_fe_1) 

tuk.cld_ft_3 <- cld(tuk_ft_3, decreasing = TRUE)   
tuk.cld_ft_3 $mcletters$Letters
```

### Helianthemum oelandicum
#### Site models
No site models: Helianthemum was only sampled in T


## Anatomy
### Fumana ericoides
#### Site models
##### Vessel density - Stems
```{r}
mod_fe_an_1 <- lm(vessel_density_per_mm2_Tige ~ site_type, data = anarchi_Fe)
mod_fe_an_1_aov <- aov(vessel_density_per_mm2_Tige ~ site_type, data = anarchi_Fe)

anova(mod_fe_an_1)
plot(mod_fe_an_1)

summary(mod_fe_an_1)
boxplot(vessel_density_per_mm2_Tige ~ site_type, data = anarchi_Fe)


tuk_fe_an_1 <- glht(mod_fe_an_1_aov, linfct = mcp(site_type = "Tukey"))
# test de Tukey:
summary(mod_fe_an_1) 

tuk.cld_fe_an_1 <- cld(tuk_fe_an_1, decreasing = TRUE)   
tuk.cld_fe_an_1 $mcletters$Letters
```
##### Mean vessel size - Stems
```{r}
mod_fe_an_2 <- lm(mean_vessel_size_µm2_Tige ~ site_type, data = anarchi_Fe)
mod_fe_an_2_aov <- aov(mean_vessel_size_µm2_Tige ~ site_type, data = anarchi_Fe)

anova(mod_fe_an_2)
plot(mod_fe_an_2)

summary(mod_fe_an_2)
boxplot(mean_vessel_size_µm2_Tige ~ site_type, data = anarchi_Fe)


tuk_fe_an_2 <- glht(mod_fe_an_2_aov, linfct = mcp(site_type = "Tukey"))
# test de Tukey:
summary(mod_fe_an_2) 

tuk.cld_fe_an_2 <- cld(tuk_fe_an_2, decreasing = TRUE)   
tuk.cld_fe_an_2 $mcletters$Letters
```
##### Theoretical conductivity - Stems
```{r}
mod_fe_an_3 <- lm(Kth_Tige ~ site_type, data = anarchi_Fe)
mod_fe_an_3_aov <- aov(Kth_Tige ~ site_type, data = anarchi_Fe)

anova(mod_fe_an_3)
plot(mod_fe_an_3)

summary(mod_fe_an_3)
boxplot(Kth_Tige ~ site_type, data = anarchi_Fe)


tuk_fe_an_3 <- glht(mod_fe_an_3_aov, linfct = mcp(site_type = "Tukey"))
# test de Tukey:
summary(mod_fe_an_3) 

tuk.cld_fe_an_3 <- cld(tuk_fe_an_3, decreasing = TRUE)   
tuk.cld_fe_an_3 $mcletters$Letters
```

### Fumana thymifolia
#### Site models
##### Vessel density - Stems
```{r}
mod_ft_an_1 <- lm(vessel_density_per_mm2_Tige ~ site_type, data = anarchi_Ft)
mod_ft_an_1_aov <- aov(vessel_density_per_mm2_Tige ~ site_type, data = anarchi_Ft)

anova(mod_ft_an_1)
plot(mod_ft_an_1)

summary(mod_ft_an_1)
boxplot(vessel_density_per_mm2_Tige ~ site_type, data = anarchi_Ft)


tuk_ft_an_1 <- glht(mod_ft_an_1_aov, linfct = mcp(site_type = "Tukey"))
# test de Tukey:
summary(mod_ft_an_1) 

tuk.cld_ft_an_1 <- cld(tuk_ft_an_1, decreasing = TRUE)   
tuk.cld_ft_an_1 $mcletters$Letters
```
##### Mean vessel size - Stems
```{r}
mod_ft_an_2 <- lm(mean_vessel_size_µm2_Tige ~ site_type, data = anarchi_Ft)
mod_ft_an_2_aov <- aov(mean_vessel_size_µm2_Tige ~ site_type, data = anarchi_Ft)

anova(mod_ft_an_2)
plot(mod_ft_an_2)

summary(mod_ft_an_2)
boxplot(mean_vessel_size_µm2_Tige ~ site_type, data = anarchi_Ft)


tuk_ft_an_2 <- glht(mod_ft_an_2_aov, linfct = mcp(site_type = "Tukey"))
# test de Tukey:
summary(mod_ft_an_2) 

tuk.cld_ft_an_2 <- cld(tuk_ft_an_2, decreasing = TRUE)   
tuk.cld_ft_an_2 $mcletters$Letters
```
##### Theoretical conductivity - Stems
```{r}
mod_ft_an_3 <- lm(Kth_Tige ~ site_type, data = anarchi_Ft)
mod_ft_an_3_aov <- aov(Kth_Tige ~ site_type, data = anarchi_Ft)

anova(mod_ft_an_3)
plot(mod_ft_an_3)

summary(mod_ft_an_3)
boxplot(Kth_Tige ~ site_type, data = anarchi_Ft)


tuk_ft_an_3 <- glht(mod_ft_an_3_aov, linfct = mcp(site_type = "Tukey"))
# test de Tukey:
summary(mod_ft_an_3) 

tuk.cld_ft_an_3 <- cld(tuk_ft_an_3, decreasing = TRUE)   
tuk.cld_ft_an_3 $mcletters$Letters
```

### Helianthemum oelandicum
No site models: Helianthemum was only sampled in T

## Anatomy and architecture
